FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-18 NewVersion/sections/RelatedWork.tex
Final sections

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model (normal inheritance and virtual inheritance). 
It allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition.
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. As far as we know there is no any formal model that
captures this aspect of the C++ method dispatching model. 
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}

>>>>

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model (normal inheritance and
virtual inheritance). \bruno{what is ``normal'' inheritance?}
C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition.
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. As far as we know there is no any formal model that
captures this aspect of the C++ method dispatching model. 
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}
